An Experimental Analysis of the Influence of the Precision of Parameters in an Artificial Neural Network

### 2025-07-16 paper/main.tex
fix

Figure~\ref{fig:grad16} shows accuracy peaked at 97.07% with a clipping value of 0.5, 
while the lowest accuracy (96.55%) occurred at clip=0.01, suggesting that very small
clip values may overly restrict gradient updates and hurt learning.
Training time ranged indicating that moderate clipping supports efficient convergence.
Evaluation time remained stable across all clip values (around 2.01s to 2.16s),
showing that clipping primarily impacts training rather than inference performance. 
Also Figure~\ref{fig:grad32} shows that accuracy was most stable across all clip values
with the highest accuracy at clip=0.5, demonstrating its robustness to gradient clipping
variations. Training time suggesting that larger clip values can speed up convergence
without sacrificing stability.
Evaluation time confirming that clipping had minimal effect on inference time.

>>>>

Figure~\ref{fig:grad16} shows accuracy peaked at 97.07\% with a clipping value
of 0.5, while the lowest accuracy (96.55\%) occurred at clip=0.01, suggesting
that very small clip values may overly restrict gradient updates and hurt
learning. Training time ranged indicating that moderate clipping supports
efficient convergence. Evaluation time remained stable across all clip values
(around 2.01s to 2.16s), showing that clipping primarily impacts training
rather than inference performance. Also Figure~\ref{fig:grad32} shows that
accuracy was most stable across all clip values with the highest accuracy at
clip=0.5, demonstrating its robustness to gradient clipping variations.
Training time suggesting that larger clip values can speed up convergence
without sacrificing stability. Evaluation time confirming that clipping had
minimal effect on inference time.
